Estimating the Financial Impact of Wildfire Smoke on US National parks

### 2020-05-21 Markdown Documents/Manuscript.Rmd
small text change

The primary goal of this project is to assess how visitation to national parks in the Inter-Mountain and Pacific regions has systematically varied with surface level concentrations of PM2.5 resulting from wildfire smoke from 1980 - 2018. Given the variability in recreational fees between parks and over time, the secondary goal of this project is to produce order of magnitude estimates of the financial losses that wildfire smoke has caused  park units during the same time period. The intention of this research is not to perform an economic analysis of smoke effects on each park specifically, but rather to provide an approximation of how wildfire smoke affects population level recreational decision making and what the downstream economic impacts have been historically and may be in the future.

>>>>

The primary goal of this project is to assess how visitation to national parks in the Inter-Mountain and Pacific regions has systematically varied with surface level concentrations of PM2.5 resulting from wildfire smoke from 1980 - 2018. Given the variability in recreational fees between parks and over time, the secondary goal of this project is to produce order of magnitude estimates of the financial losses that wildfire smoke has caused  park units during the same period. The intention of this research is not to perform an economic analysis of smoke effects on each park specifically, but rather to provide an approximation of how wildfire smoke affects population level recreational decision making and what the downstream economic impacts have been historically and may be in the future.
